A Collection of Thoughts on the Keccak/SHA-3 Construction

### 2018-04-29 s2018-math490/thesis/thesis.tex
thesis
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

    Within this section are a series of introductions which provide necessary
background on the topics of cryptography, hash functions, the development of
Keccak/SHA-3, and its structure. While certain sections can be skipped if the
reader has the prerequisite knowledge, hopefully all readers find the material
engaging and useful. Following these introductions, this paper presents the
analysis of the Keccak/SHA-3 hash function before concluding with a final
evaluation and further work.

@@

\subsection{Introduction on the Topics of Cryptography} \label{sec:i:crypto}

@@

    Prior to the late 19th century, cryptography was split into three major
branches: ciphers, codes, and stenography.

\subsection{Introduction on the Topics of Hash Functions} \label{sec:i:hash}

    Within cryptography's collection of algorithms, few are are as useful as
hash functions have proven to be to cryptographers and non-cryptographers
alike. A hash function maps arbitrary length binary strings to binary strings
of a fixed length.

>>>>

    Within this section are a series of introductions which provide necessary
background on the topics of cryptographic hash functions, the development of
Keccak/SHA-3, and its structure. While certain sections can be skipped if the
reader has the prerequisite knowledge, hopefully all readers find the material
engaging and useful. Following these introductions, this paper presents the
analysis of the Keccak/SHA-3 hash function before concluding with a final
evaluation and further work.

@@

\subsection{Introduction on the Topics of Cryptographic Hash Functions} \label{sec:i:hash}

@@

    Within cryptography's collection of algorithms, few are as useful as
hash functions have proven to be to cryptographers and non-cryptographers
alike. A hash function maps arbitrary length binary strings to binary strings
of a fixed length. Because the inputs are of arbitrary size, by the pigeonhole
principle, there must exist at least one collision. However, to be considered
cryptographically secure, finding such a collision must be hard (on the order
of $2^{\frac{b}{2}}$ for $b$ the number of bits in the output).

    Further, a cryptographic hash function must be resistant finding a
preimage: for a given output value $v$, finding an input $x$ such that
$f(x) = v$ should be roughly on the order of $2^{b}$.
